Figure 3 normalization

### 2019-11-27 main_figures/doublets.Rmd
renamed main figures, updated filtering and dimensionality figures

```{r, fig.height=6, fig.width=7}
plot_grid( plot_grid(p1, p2, nrow=1, labels=LETTERS[1:2]), plot_grid(p3, p4, nrow=1, labels=LETTERS[3:4], rel_widths=c(2,3)), nrow=2)
```

>>>>

```{r figure1, fig.height=6, fig.width=7}
plot_grid( plot_grid(p1, p2, nrow=1, labels=LETTERS[1:2]), plot_grid(p3, p4, nrow=1, labels=LETTERS[3:4], rel_widths=c(2,3)), nrow=2)
```

### 2019-11-27 main_figures/normalization.Rmd
renamed main figures, updated filtering and dimensionality figures

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
})
suppressMessages(devtools::load_all("../../pipeComp/"))
source("../misc_functions.R")
theme_set(theme_cowplot(font_size = 11))
```

@@

```{r}
p1 <- scrna_evalPlot_DR(res, "covarRes", agg.by = "norm", anno_legend=FALSE) +
    scrna_evalPlot_DR(res, "covarRes", covar = "log10_total_features", agg.by = "norm", anno_legend=FALSE)
p1 <- grid.grabExpr(draw(p1))

p2 <- grid.grabExpr(draw(
  scrna_evalPlot_DR(res, what="silhouette", agg.by = "norm", value_format = "", show_heatmap_legend = TRUE)))

H <- scrna_evalPlot_clustAtTrueK(res, "ARI", agg.by = "norm", scale = TRUE, reorder_rows = TRUE, anno_legend=FALSE)
H <- H + scrna_evalPlot_clust(res, "MI", agg.by = "norm", scale = TRUE, reorder_rows=row.names(H@matrix), anno_legend=FALSE)
p3 <- grid.grabExpr(draw(H))
```

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(matrixStats)
})
suppressMessages(devtools::load_all("../../pipeComp/"))
source("../misc_functions.R")
theme_set(theme_cowplot(font_size = 11))
renameNorm <- function(x){
  .renameHrows(x, f=function(x){
    x <- gsub("^norm\\.", "", x)
    x <- gsub("seuratvst","sctransform",x)
    x <- gsub(".noscale", " (no scaling)", x)
  })
}
```

@@

```{r}
p1 <- scrna_evalPlot_DR(res, "covarRes", agg.by = "norm", anno_legend=FALSE, reorder_rows = TRUE)
p1 <- p1 + scrna_evalPlot_DR(res, "covarRes", covar = "log10_total_features", agg.by = "norm", anno_legend=FALSE, reorder_rows=p1)
p1 <- grid.grabExpr(draw(renameNorm(p1)))

p2 <- grid.grabExpr(draw(
  renameNorm(scrna_evalPlot_DR(res, what="silhouette", agg.by = "norm", value_format = "", show_heatmap_legend = TRUE))))

H <- scrna_evalPlot_clustAtTrueK(res, "ARI", agg.by = "norm", scale = TRUE, reorder_rows = TRUE, anno_legend=FALSE)
H <- H + scrna_evalPlot_clust(res, "MI", agg.by = "norm", scale = TRUE, reorder_rows=row.names(H@matrix), anno_legend=FALSE)
p3 <- grid.grabExpr(draw(renameNorm(H)))
```
